Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 method.tex
Added notation for detection statistic
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@857 ccdd05d5-56c1-461a-bf98-85f6876523b4

\editorial{This paragraph is hereby condemned!  It's too early to introduce this equation, and this should be more of a summary of our method.}In order to minimize latency we propose using the time-domain convolution
presented in \eqref{eq:SNRTD}.  However, because the brute-force evaluation of
\eqref{eq:SNRTD} is far too costly to be useful, we will consider an
approximation to \eqref{eq:SNRTD} that can reduce substantially the cost of
\realtime\ filtering. This approximation has the form
%
% orthogonal decomposition filtering
%
\begin{equation}
\rho_i(t) \approx \sum_k^{\numslices} \sum_j^{\numsvdtmps} 
	\int_{\tau_{k}}^{\tau_{k+1}} v_{ijk} \sigma_{jk} u_{jk}\,(\tau) \, h(t-\tau) \, d \tau \label{eq:decomp}
\end{equation} 
%
%
where $u_{jk}(\tau)$ is an orthogonal basis set of filters spanning the space
of $\{x_i(\tau)\}$ and $\sigma_{jk} v_{ijk}$ is a tensor relating the filters
$u_{jk}(\tau)$ to the original filter set $\{x_i(\tau)\}$.  We claim that with
a suitable choice of filters $u_{jk}(\tau)$ one can reduce the computational
cost of \eqref{eq:SNRTD} sufficiently to feasibly search for
gravitational waves from compact binary coalescence in \realtime.  This
requires 1) exploiting
the time-frequency characteristics of the binary waveforms and 2) exploiting the redundancy of the template bank. We describe our
procedure for producing the decompostion in \eqref{eq:decomp} in the remainder
of this section.

>>>>

\editorial{I just dropped our new notation in here; I haven't edited the text yet.}%
Definition of decimated detector data:
\begin{equation}
	x^{s+1}[k] = \left( H^\shortdownarrow x^s\right)[k]
\end{equation}

In order to minimize latency we propose using the time-domain convolution
presented in \eqref{eq:SNRTD}.  However, because the brute-force evaluation of
\eqref{eq:SNRTD} is far too costly to be useful, we will consider an
approximation to \eqref{eq:SNRTD} that can reduce substantially the cost of
\realtime\ filtering. This approximation has the form
%
% orthogonal decomposition filtering
%
\begin{equation}
	\rho_i^s [k] =%
		% Reconstruction
		\underbrace{
			\sum_{\mathclap{l=0}}^{\mathclap{L^s-1}} v_{il}^s \sigma_l^s
		}_\textrm{\clap{reconstruction}}
		% Orthogonal FIR filter
		\overbrace{
			\sum_{\mathclap{n=0}}^{\mathclap{N^s-1}} u_l^s[n] x^s[k-n]
		}^\textrm{\clap{orthogonal {\sc fir} filters}}
		% Plus ...
		+
		% Interpolation SNR
		\underbrace{
			\left(H^\uparrow \rho_i^{s+1}\right)[k]
		}_\textrm{\clap{{\sc snr} from previous time slices}}
\end{equation}
%
%
where $u_{jk}(\tau)$ is an orthogonal basis set of filters spanning the space
of $\{x_i(\tau)\}$ and $\sigma_{jk} v_{ijk}$ is a tensor relating the filters
$u_{jk}(\tau)$ to the original filter set $\{x_i(\tau)\}$.  We claim that with
a suitable choice of filters $u_{jk}(\tau)$ one can reduce the computational
cost of \eqref{eq:SNRTD} sufficiently to feasibly search for
gravitational waves from compact binary coalescence in \realtime.  This
requires 1) exploiting
the time-frequency characteristics of the binary waveforms and 2) exploiting the redundancy of the template bank. We describe our
procedure for producing the decompostion in \eqref{eq:decomp} in the remainder
of this section.
